---
title: "Rate of Change of Variables Over Time"
output: html_notebook
---

Job Reallocation Rate as defined and collected by Business Employment Dynamics is based on the formula:

$$Job \; Reallocation \; Rate = \frac{gain + loss}{total\;employment}$$

Using the formula $rate = \frac{final-initial}{initial}$, the rate of change of the variables are calculated to indentify if there are discernable relationships in them. 

# Rate of Change of Training Indices Over Time
## Rate of Change for Required Level of Education
```{r}
lmod <- lm(dRL ~ period.num, t)
summary(lmod)
```
## Rate of Change for On-the-job Training
```{r}
lmod <- lm(dOJ ~ period.num, t)
summary(lmod)
```
## Rate of Change for In-Plant Training
```{r}
lmod <- lm(dPT ~ period.num, t)
summary(lmod)
```
## Rate of Change for Relevant Work Experience
```{r}
lmod <- lm(dRW ~ period.num, t)
summary(lmod)
```

According to the results, there is little to no statistical relationship between the variables over time. The changes are also minimal, at less than |1%|. 

```{r}
ggplot(data = t) + 
  geom_point(mapping = aes(x = period.num, y = dRW, colour = factor(NAICS))) + 
  ggtitle("Rate of Change of RW Over Time")
```

Visualizing the data allows us to see that the fluctuations are relatively small across industry. 

# Rate of Change of Job Reallocation Rates Over Time
## Rate of Change for Job Reallocation Rate
```{r}
lmod <- lm(dadj_realloc ~ period.num, t)
summary(lmod)
```
## Rate of Change for Job Gains Rate
```{r}
lmod <- lm(dgain ~ period.num, t)
summary(lmod)
```
## Rate of Change for Job Loss Rate
```{r}
lmod <- lm(dloss ~ period.num, t)
summary(lmod)
```

For job reallocation rate and its components, it has relatively weak relationship. Nevertheless, it is interesting that the rate is mostly positive even though the rates as a whole has a negative relationship with the variables over time. 

Visualizing the data, the fluctuations in general are also small except for Mining (NAICS 21), whose values are large relative to other industries. 

```{r}

ggplot(data = t) + 
  geom_point(mapping = aes(x = period.num, y = dadj_realloc, colour = factor(NAICS))) + 
  ggtitle("Rate of Change of Job Reallocation Rate Over Time")
```

